---
title: "Day 4 Lab Exercise"
output: html_notebook
---

```{r setup,  include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

## 5.4.1 Exercise

### #1

Find all flights that

(1) Had an arrival delay of two or more hours
```{r}
flights_arr_delay <- <FILL-IN>
```
```{r}
summary(flights_arr_delay$arr_delay) # check the variable, arr_delay
```


(2) Flew to Houston (IAH or HOU)
```{r}
flights_iah_hou <- 
```

```{r}
factor(flights_iah_hou$dest) %>% 
  levels() # level check
```

(3) Were operated by United, American, or Delta
```{r}
airlines # check airlines' two letter abbr. to find their carrier codes

<FILL-IN>
```


(4) Departed in summer (July, August, and September)
```{r}
flights_7_9 <- <FILL-IN>

levels(factor(flights_7_9$month)) # level check
```

(5) Arrived more than two hours late, but didn’t leave late
```{r}
<FILL-IN>

```


(6) Were delayed by at least an hour, but made up over 30 minutes in flight

```{r}
<FILL-IN>
```

(7) Departed between midnight and 6am (inclusive)
```{r}
<FILL-IN>
```

## 5.3.1 Exercise

### #1. How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).

```{r}
<FILL-IN>
```


### #3 Sort flights to find the fastest (highest speed) flights.

```{r}
<FILL-IN>
```

## 5.4.1 Exercises
### #2 What happens if you include the name of a variable multiple times in a select() call?
```{r}
<FILL-IN>
```

## 5.6.7 Exercises
### #5 Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
```{r}
<FILL-IN>
# But is this true? Think about it!
```

